---
name: Faezeh
surname: Arab Hassani
position: "Research Fellow"
address: "Department of Electrical and Computer Engineering, National University of Singapore"
# phone: +1 22 3333 4444
# www: mariecurie.com
# email: "Marie.Curie@ens.fr"
# twitter: mariecurie
github: FaezehAHassani
linkedin: Faezeh Arab Hassani
googlescholar: Faezeh A Hassani
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#tinytex::install_tinytex()
library(vitae)
```

# Summary

 * **Experience:** Forward-thinking and accomplished electronics research scientist with 7+ years of experience
 * **Skills:** A strong background in the design, fabrication, and characterization of micro/nano-electronic devices leading to successful generation of products for environmental and healthcare technology
 * **Career Highlights:**
   * Attracted 2 research funding, and 2 awards
   * More than 30 peer reviewed scientific publications
   * Managed a clean room facility at National University of Singapore
   * Advised 4 M.Sc. graduate students, and lectured 3 graduate courses
   * Gave 4 invited talks at the international conferences
   * Presented at 10 international and local conferences
   * Reviewer, and associate editor of international journals
   * Chaired a session at 1 international conference
   * Organized a local scientific workshop with 50 attendees
   * Woman in engineering coordinator of IEEE UK student Branch

# Eexperience
```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, 
  "JSPS postdoctoral researcher", "2012-13", "Japan Advanced Institute of Science and Technology", "Japan",
  "Reserach fellow", "2013-14", "National University of Singapore", "Singapore", 
  "Postdoctoral research associate", "2014-16", "University of Sheffiled", "United Kingdom",
 "Reserach fellow", "2016-19", "National University of Singapore", "Singapore", 
 "JSPS invitational researcher", "2019-20", "Japan Advanced Institute of Science and Technology", "Japan",
 "Reserach fellow", "2020-current", "National University of Singapore", "Singapore" 
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Education
```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, 
  #"Bachelor of Electrical Engineering (Electronics)", "1894", "Sorbonne Université", #"Iran",
  "Master of Electrical and Electronics Engineering", "2005-08", "University of Tehran", "Tehran, Iran", 
  "PhD of Electrical and Electronics Engineering", "2008-12", "University of Southampton", "Southampton, United Kingdom"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Fellowships and awards
```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2008, "PhD studentship, University of Southampton", "Awarding body: European FP7 NEMSIC project and University of Southampton",
  2012, "JSPS postdoctoral fellowship, Japan Advanced Institute of Science and Technology", "Awarding body: Japan Society for the Promotion of Science",
  2016, "Santander research mobility award, University of Sheffield", "Awarding body: University of Sheffield",
  2019, "JSPS invitational fellowship, The University of Tokyo", "Awarding body: Japan Society for the Promotion of Science"
) %>% 
  brief_entries(
    glue::glue("{Type}"),
    Year, 
    Desc
  )
```

# Skills
• Micro/nano-fabrication • Semiconductors • MEMS/NEMS • Energy harvesting • Flexible Electronics • Sensors and Actuators • ex vivo and in vivo • Finite Element Analysis (FEA) • Biomedical devices

# Scientific affiliations
 
• Member of Japan Society of Applied Physics • Senior Member of IEEE
 

# Hobbies
 
• Painting • Badminton • Nature walking

# Publications
Please check: https://scholar.google.com/citations?user=Veva8EAAAAAJ&hl=en
